Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-10 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Reviewer 2: eta-expansion

The natural deduction calculus proposed and used here has standard rules for propositional connectives and quantifiers, as shown in Figures \ref{fig:PropositionalRules} and \ref{fig:QuantifierRules}. The extension to classical logic is achieved by adding a rule for double negation elimination, shown in Figure \ref{fig:Classical}, and $\beta$-reduction is handled by the $\beta$ rule shown in Figure \ref{fig:ReductionRules}.
Finally, modal operators are handled by special new rules that insert or remove formulas from boxes, as shown in Figure \ref{fig:NDK}.
A \emph{derivation} is a directed acyclic graph whose nodes are formulas and whose edges correspond to applications of the inference rules. A \emph{proof} of a formula $F$ is a derivation without open assumptions and having $F$ as root not inside any box.

>>>>

The natural deduction calculus proposed and used here has standard rules for propositional connectives and quantifiers, as shown in Figures \ref{fig:PropositionalRules} and \ref{fig:QuantifierRules}. The extension to classical logic is achieved by adding a rule for double negation elimination, shown in Figure \ref{fig:Classical}, and $\beta$-reduction\footnote{Rules for $\eta$-expansion \citep{BenzmuellerBrownKohlhase} are not included here, because they are not needed in the ontological arguments.} is handled by the $\beta$ rule shown in Figure \ref{fig:ReductionRules}.
Finally, modal operators are handled by special new rules that insert or remove formulas from boxes, as shown in Figure \ref{fig:NDK}.
A \emph{derivation} is a directed acyclic graph whose nodes are formulas and whose edges correspond to applications of the inference rules. A \emph{proof} of a formula $F$ is a derivation without open assumptions and having $F$ as root not inside any box.
